On particular diameter bounds for integral point sets in higher dimensions

### 2019-10-21 AvdMomZvol_rails/Article.tex
Last iteration

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage[russian,english]{babel}
\usepackage{amsmath,amsfonts,amssymb,euscript,graphicx,wrapfig,multirow}
\usepackage{dsfont}
\usepackage{amsthm}
\inputencoding{utf8}
\bibliographystyle{unsrt}
\textheight=240mm \textwidth=170mm
\hoffset=-17mm
\voffset=-17mm

@@

\begin{center}
\emph{Voronezh State University}
\end{center}

Avdeev N.N., Zvolinsky R.E., Momot E.A.

On particular diameter bounds for integral point sets in higher dimensions

@@

\begin{theorem}
	Let $\mathcal{P}$ be a planar integral point set consisting of
	$n - 2$ points on line $l$ and two points $P_{1}$ and $P_{2}$ on a
	parallel line $m$ with distance $r$ between $l_{1}$ and $l_{2}$. If there
	exist positive integers $v$, $w$ with $f^{2} + v^{2}
	= w^{2}$ and $v < 2r$, where $|P_{1}P_{2}| = f$,
	then

@@

\bibliography{literature}

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage[russian,english]{babel}
\usepackage{amsmath,amsfonts,amssymb,euscript,graphicx,wrapfig,multirow}
\usepackage{dsfont}
\usepackage{amsthm}
\inputencoding{utf8}
%\bibliographystyle{unsrt}
\textheight=240mm \textwidth=170mm
\hoffset=-17mm
\voffset=-17mm

\usepackage[backend=biber,style=gost-numeric,sorting=none]{biblatex}
\addbibresource{../common/notmy.bib}
\addbibresource{../common/my.bib}

@@

\title{
	On particular diameter bounds for integral point sets in higher dimensions
	%\footnote{
	%	This work was carried out at Voronezh State University and supported by the Russian Science
	%	Foundation grant 19-11-00197.
	%}
}

%% Прекрасно понимаю, что следующая команда - дичь и вордописчество, но время не ждёт, время жмёт
\author{
	Avdeev N.N.
	\footnote{nickkolok@mail.ru, avdeev@math.vsu.ru}
	, Zvolinsky R.E., Momot E.A.
	\\
	\\
	\emph{Voronezh State University}
}

\maketitle

@@

\begin{theorem}
	Let $\mathcal{P}$ be a planar integral point set consisting of
	$n - 2$ points on line $l_1$ and two points $P_{1}$ and $P_{2}$ on a
	parallel line $l_2$ with distance $r$ between $l_{1}$ and $l_{2}$. If there
	exist positive integers $v$, $w$ with $f^{2} + v^{2}
	= w^{2}$ and $v < 2r$, where $|P_{1}P_{2}| = f$,
	then

@@

\printbibliography
%\bibliography{literature}
